### 2014-10-14 fundamentals/intro.tex
intro done

In order to characterize the performance of nuclear fuel cycle tecnhologies and performance metrics, nuclear fuel cycle analysis 
requires calculation and optimization of myriad physical, nuclear, chemical, 
industrial, and political phenomena. Furthermore, complex systems such as 
nuclear process physics, facility deployment, and material routing each 
must be modeled simultaneously for even the simplest of nuclear fuel cycle 
simulations.

% MJG - I'm hesitant about using the phrase 'full detail'. I think we can be
% more precise.

Historically, nuclear fuel cycle simulators have addressed this with software 
ranging from spreadsheet driven flow calculators to high-fidelity industrial 
models. To date, current tools are either static, fleet-based, or 
privately distributed. An alternative to these approaches is a dynamic, 
agent-based simulator with an open platform.

Modern insight indicates that dynamic nuclear fuel cycle analysis more 
realistically supports a broader range of simulation goals than static analysis 
\cite{piet_dynamic_2011}. Similarly, experience in the greater field of systems 
analysis indicates that agent-based modeling enables more flexible simulation 
control, without loss of generality \cite{thatpapermattsent}. Finally, 
openness allows cross-institutional collaboration, increases code robustness, 
and enables the cultivation of an ecosystem of calculation options, 
\cite{softwarecarpentryresource}.

The fundamental concepts of the \Cyclus nuclear fuel cycle simulator capture 
these modern insights so that challenges in nuclear fuel cycle analysis can be 
better addressed.

>>>>

As nuclear power expands both domestically and internationally, nuclear fuel cycle
performance analysis on technical, economic, political, and environmental axes increases 
in importance. Appropriate nuclear fuel cycle analysis requires calculation of myriad physical, nuclear, 
chemical, industrial, and political phenomena. Nuclear fuel cycle simulators 
therefore couple complex systems such as nuclear process physics, 
facility deployment, and material routing. However, most nuclear fuel cycle 
simulators have not incorporated modern insights in simulation science and 
software architecture that can enable more efficient, accurate, robust, and 
validated analysis. The Cyclus Nuclear Fuel Cycle Simulator Framework and 
its modeling ecosystem answer the need for a next generation nuclear fuel cycle 
simulator.

Historically, nuclear fuel cycle simulators have estimated 
nuclear fuel cycle performance using software 
ranging from ad hoc spreadsheet-driven flow calculators to highly specialized 
proprietary models. To date, current tools are either static, fleet-based, 
privately distributed, or all of the above. Each of these qualities present a 
severe challenge to modeling fidelity, generality, effciiency, robustness, and 
scientific transparency.

An alternative to these approaches is a dynamic, agent-based simulator with an 
open platform and an ecosystem of research-driven capabilities.  Modern 
insight indicates that dynamic nuclear fuel cycle analysis more realistically 
supports a broader range of simulation goals than static analysis 
\cite{piet_dynamic_2011}. Similarly, experience in the greater field of systems 
analysis indicates that agent-based modeling enables more flexible simulation 
control, without loss of generality \cite{thatpapermattsent}. Finally, openness 
allows cross-institutional collaboration, increases code robustness, and 
enables the cultivation of an ecosystem of calculation options, 
\cite{softwarecarpentryresource}.  The fundamental concepts of the \Cyclus 
nuclear fuel cycle simulator capture these modern insights so that challenges 
in nuclear fuel cycle analysis can be better addressed.
